---
title: "Gender transfer at the language level"
output: html_document
---

Read the packages
```{r}
library(tidyverse)
options(scipen = 5)
```

## 3.1 Gender transfer between all systems


Read the data
```{r}
data <- read.csv("data.ttests.csv")
```


Run t-test between raw accuracy and baseline for languages within Indo-European
```{r}
# extract raw accuracy
data %>% filter(type == "raw_acc" & !source %in% c("stan1318","hebr1245") &  !target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value)) -> raw_acc
# extract baseline
data %>% filter(type == "baseline" & !source %in% c("stan1318","hebr1245") & !target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value))-> baseline
# run t-tests
t.test(raw_acc$value, baseline$value, paired = T)
```

Run the same but from Afro-Asiatic languages to Indo-European languages
```{r}
# extract raw accuracy
data %>% filter(type == "raw_acc" & source %in% c("stan1318","hebr1245") &  !target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value)) -> raw_acc
# extract baseline
data %>% filter(type == "baseline" & source %in% c("stan1318","hebr1245") & !target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value))-> baseline
# run t-test
t.test(raw_acc$value, baseline$value, paired = T)
```

Run the same but from Indo-European languages to Afro-Asiatic languages
```{r}
# extract raw accuracy
data %>% filter(type == "raw_acc" & !source %in% c("stan1318","hebr1245") &  target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value)) -> raw_acc
# extract baseline
data %>% filter(type == "baseline" & !source %in% c("stan1318","hebr1245") & target %in% c("stan1318","hebr1245")) %>% group_by(source, target, type) %>% summarise(value = mean(value))-> baseline
# run t-test
t.test(raw_acc$value, baseline$value, paired = T)
```

Read the data and run the regression for phylogenetic distance
```{r}

# adjust format
data.reg$System_source <- factor(data.reg$System_source)
# run regression
model <- lm(Accuracy ~ PhyloDist, data = data.reg)
# visualize results
summary(model)
```

## 3.2 Gender transfer between isomorphicsystems

Read the data again to run the regression for phylogenetic distance and system types
```{r}
# read data
data.reg <- read.csv("data.reg.phylodist.system.csv")
# run regression
glm.fit <- lm(Accuracy ~ PhyloDist*System_source,
               data = data.reg)
# visualize results
summary(glm.fit)
```

